%!TEX program = pdflatex
\documentclass[10.5pt, a4paper]{article}

% ----------- Encoding & Font ---------------------------------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[scaled=0.92]{helvet}
\renewcommand{\familydefault}{\sfdefault}

% ----------- Layout ------------------------------------------
\usepackage[left=0.48in, right=0.48in, top=0.25in, bottom=0.2in]{geometry}

% ----------- Packages ----------------------------------------
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{array}
\usepackage{tabularx}
\usepackage{microtype}

% ----------- Color Palette -----------------------------------
\definecolor{cvnavy}  {RGB}{15,  55, 110}
\definecolor{cvsteel} {RGB}{52,  90, 150}
\definecolor{cvdark}  {RGB}{38,  38,  38}
\definecolor{cvgray}  {RGB}{95, 105, 120}
\definecolor{cvgrayline}  {RGB}{195, 210, 228}

% ----------- Hyperlinks --------------------------------------
\hypersetup{colorlinks=true, urlcolor=cvsteel, linkcolor=cvsteel, pdfencoding=auto}

% ----------- Section Style -----------------------------------
\titleformat{\section}
  {\fontsize{9pt}{11pt}\bfseries\color{cvnavy}\MakeUppercase}
  {}{0em}{}
  [\vspace{2pt}{\color[RGB]{195,210,228}\hrule height 0.75pt}\vspace{0.5pt}]
\titlespacing{\section}{0pt}{4pt}{2pt}

% ----------- Global ------------------------------------------
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\color{cvdark}

% ----------- Bullets -----------------------------------------
\setlist[itemize]{
  leftmargin=1.15em,
  itemsep=0.5pt,
  parsep=0pt,
  topsep=1.5pt,
  label={\color{cvsteel}\small$\bullet$}
}

% ----------- Experience Entry --------------------------------
\newcommand{\expentry}[4]{%
  \vspace{0.5pt}%
  \begin{tabularx}{\linewidth}{@{} X r @{}}
    {\fontsize{10pt}{12pt}\selectfont\bfseries\color{cvdark} #1}
    \enspace{\textcolor[RGB]{195,210,228}{$|$}}\enspace
    {\fontsize{9pt}{11pt}\selectfont\color{cvgray} #2}
    &
    {\fontsize{8.5pt}{10pt}\selectfont\color{cvgray} #3}
  \end{tabularx}%
  \ifx&#4&\else
    \par\vspace{0.5pt}{\fontsize{8.5pt}{10pt}\selectfont\color{cvgray} #4}%
  \fi
  \vspace{1pt}%
}

% ----------- Project Entry -----------------------------------
\newcommand{\projentry}[3]{%
  \vspace{0.5pt}%
  \begin{tabularx}{\linewidth}{@{} X r @{}}
    {\fontsize{10pt}{12pt}\selectfont\bfseries\color{cvdark} #1}
    &
    {\fontsize{8.5pt}{10pt}\selectfont\color{cvgray} #2}
  \end{tabularx}%
  \par\vspace{0.5pt}%
  {\fontsize{8.5pt}{10pt}\selectfont\color{cvsteel}\href{#3}{#3}}%
  \vspace{1pt}%
}

% ----------- Education Entry ---------------------------------
\newcommand{\eduentry}[4]{%
  \vspace{0.5pt}%
  \begin{tabularx}{\linewidth}{@{} X r @{}}
    {\fontsize{10pt}{12pt}\selectfont\bfseries\color{cvdark} #1}
    \enspace{\textcolor[RGB]{195,210,228}{$|$}}\enspace
    {\fontsize{9pt}{11pt}\selectfont\color{cvgray} #2}
    &
    {\fontsize{8.5pt}{10pt}\selectfont\color{cvgray} #3}
  \end{tabularx}%
  \par\vspace{0.5pt}%
  {\fontsize{9pt}{11pt}\selectfont\color{cvgray} #4}%
  \vspace{1pt}%
}

% =============================================================
\begin{document}
\pagestyle{empty}

% ----------- HEADER ------------------------------------------
\begin{center}
  {\fontsize{20pt}{24pt}\selectfont\bfseries\color{cvnavy} Kshitij Bhardwaj}\\[3pt]
  {\fontsize{10.5pt}{13pt}\selectfont\color{cvgray} Full Stack Engineer}\\[4pt]
  {\fontsize{9pt}{11pt}\selectfont\color{cvgray}
    \href{mailto:Kshitijbhardwajkb28@gmail.com}{Kshitijbhardwajkb28@gmail.com}%
    \enspace{\textcolor[RGB]{195,210,228}{$|$}}\enspace%
    +91 97299 16844%
    \enspace{\textcolor[RGB]{195,210,228}{$|$}}\enspace%
    \href{https://kshitijkb28.github.io}{kshitijkb28.github.io}%
    \enspace{\textcolor[RGB]{195,210,228}{$|$}}\enspace%
    \href{https://www.linkedin.com/in/kshitij-bhardwaj-067240232}{LinkedIn}%
    \enspace{\textcolor[RGB]{195,210,228}{$|$}}\enspace%
    \href{https://github.com/Kshitijkb28}{GitHub}%
  }
\end{center}

\vspace{1pt}

% ----------- SUMMARY -----------------------------------------
\section{Professional Summary}

{\fontsize{9pt}{11.5pt}\selectfont
Dedicated and results-oriented \textbf{Full Stack Engineer with 2+ years of experience} building scalable web applications and AI-powered systems. Experienced in backend development using \textbf{Python, Node.js, and Laravel}, with modern frontend skills in \textbf{React and JavaScript}. Skilled in \textbf{LLM post-training, prompt engineering, API development, and cloud deployment}. Focused on delivering high-quality, reliable solutions across the full stack.
}

% ----------- TECHNICAL SKILLS --------------------------------
\section{Technical Skills}

{\fontsize{9pt}{11.5pt}\selectfont
{\renewcommand{\arraystretch}{1.25}%
\begin{tabularx}{\linewidth}{@{}
    >{\bfseries\color{cvnavy}\raggedright\arraybackslash} m{2.8cm}
    X
  @{}}
  Languages      & PHP, Python, JavaScript, C++ \\
  Frontend       & HTML, CSS, Bootstrap, JavaScript, React \\
  Backend        & Laravel, Node.js, FastAPI, Flask \\
  Databases      & MySQL, MongoDB, PostgreSQL \\
  Cloud \& Tools & AWS S3, Linux Server Setup, Git, Docker \\
  AI / LLM       & LLM Post-Training, Prompt Engineering, Model Evaluation, Dataset Preparation \\
\end{tabularx}}
}

% ----------- PROFESSIONAL EXPERIENCE -------------------------
\section{Professional Experience}

\expentry{Full Stack Engineer}{Ethara AI}{Jan 2026 -- Present}{Gurugram, India}
{\fontsize{9pt}{11.5pt}\selectfont
\begin{itemize}
  \item Building APIs and backend systems using \textbf{Python (FastAPI / Flask)} for AI-powered applications.
  \item Contributing to \textbf{LLM post-training workflows} -- dataset preparation, evaluation pipelines, and response quality improvement.
  \item Developing internal tools to support \textbf{AI model evaluation and prompt optimization}.
  \item Integrating LLM capabilities into products for intelligent automation and enhanced user experiences.
  \item Collaborating with cross-functional teams to improve AI system performance and reliability.
\end{itemize}
}

\vspace{1pt}

\expentry{Software Engineer}{Mind2web LLP}{Aug 2023 -- Oct 2025}{}
{\fontsize{9pt}{11.5pt}\selectfont
\begin{itemize}
  \item Configured and deployed multiple production projects on servers, ensuring optimal performance.
  \item Fixed critical bugs and optimized backend code to improve scalability and system reliability.
  \item Set up \textbf{Linux servers} and configured environments (Apache, Nginx, PHP, Node.js).
  \item Implemented security configurations, monitoring systems, and performance optimization strategies.
\end{itemize}
}

% ----------- PROJECTS ----------------------------------------
\section{Projects}

\projentry{Yot Ecommerce}{Jan 2025 -- Oct 2025}{https://fuse.systems}
{\fontsize{9pt}{11.5pt}\selectfont
\begin{itemize}
  \item Improved product search, workflows, and notifications using \textbf{Meilisearch, Ragic DB, and Twilio}.
  \item Developed product management modules with \textbf{secure OAuth2 authentication}.
  \item Built background jobs to fetch supplier data and auto-update product listings.
  \item Implemented optimized \textbf{PostgreSQL queries} to retrieve and display listing data efficiently.
\end{itemize}
}

\vspace{1pt}

\projentry{Remodely}{Oct 2024 -- Dec 2025}{https://remodely.com}
{\fontsize{9pt}{11.5pt}\selectfont
\begin{itemize}
  \item Built \textbf{service booking modules and admin dashboards} for bathroom and interior design services.
  \item Improved UI functionality and integrated backend services for seamless booking management.
\end{itemize}
}

\vspace{1pt}

\projentry{Service Points}{Oct 2023 -- Oct 2024}{https://app.servicepoints.nl}
{\fontsize{9pt}{11.5pt}\selectfont
\begin{itemize}
  \item Built and integrated \textbf{chatbot functionalities} using prompt engineering techniques.
  \item Developed real-time chat features using \textbf{WebSockets and CKEditor} in Node.js.
  \item Built performance monitoring charts showing \textbf{7-day page load trends} via automated cURL requests.
  \item Resolved UI inconsistencies to improve visual quality and usability across the application.
\end{itemize}
}

% ----------- EDUCATION ----------------------------------------
\section{Education}

\eduentry{B.Tech -- Computer Science}{Panipat Institute of Engineering and Technology}{Jul 2019 -- Jun 2023}{Score: 67.4\%}

\vspace{1pt}

\eduentry{12th -- Science}{Hindu Vidya Peeth}{Mar 2018 -- Mar 2019}{Score: 64\%}

\end{document}
